Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2021-01-19 journal paper/content/related_work.tex
more space saving edits

A long line of work from electrical engineering and computer science, starting from
\citet{MultiPlayerMAB-Poor08,MultiPlayerMAB-Liu10}, focuses on competition for resources, not competition for consumers. Specifically, this literature targets an application to \emph{cognitive radios}, where multiple radios transmit simultaneously in a shared medium and compete for bandwidth. Each radio chooses channels over time using a multi-armed bandit algorithm. This work studies a repeated game between bandit algorithms, and focuses on designing algorithms which work well in this game, under various assumptions on communication, synchronization and collisions.

@@

%\asedit{While we use first-mover advantage and agents' decision rule,} classic ``market competitiveness" measures, such as the Lerner Index or the Herfindahl-Hirschman Index
%\citep{tirole1988theory}, are not applicable to our setting, as they rely on ex-post observable market attributes such as prices or market shares (which are, resp., absent and endogenous for us).

>>>>

A long line of work from electrical engineering and computer science, starting from
\citet{MultiPlayerMAB-Poor08,MultiPlayerMAB-Liu10}, focuses on competition for resources, not competition for consumers. Specifically, this literature targets an application to \emph{cognitive radios}, where multiple radios transmit simultaneously in a shared medium and compete for bandwidth. Each radio chooses channels over time using a multi-armed bandit algorithm. This work studies a repeated game between bandit algorithms, and focuses on designing algorithms which work well in this game\gadelete{, under various assumptions on communication, synchronization and collisions}.

@@

\asedit{While we use first-mover advantage and agents' decision rule,} classic ``market competitiveness" measures, such as the Lerner Index or the Herfindahl-Hirschman Index
\citep{tirole1988theory}, are not applicable to our setting, as they rely on ex-post observable market attributes such as prices or market shares (which are, resp., absent and endogenous for us).

### 2021-01-19 journal paper/content/sec-model.tex
more space saving edits

\xhdr{Competition game.}
Some of our results explicitly study the game between the two principals, termed the \emph{competition game}. We model it as a simultaneous-move game: before the first agent arrives, each principal commits to an MAB algorithm. (Since MAB algorithms can be randomized, we make no distinction between pure and mixed strategies.) Principals are risk-neutral and their utility is defined as their market share, \ie the number of agents that chose this principal. Thus they aim to select the algorithm that maximizes their expected market share.

>>>>

\xhdr{Competition game.}
Some of our results explicitly study the game between the two principals, termed the \emph{competition game}. We model it as a simultaneous-move game: before the first agent arrives, each principal commits to an MAB algorithm. (Since MAB algorithms can be randomized, we make no distinction between pure and mixed strategies.) Principals are risk-neutral and their utility is defined as their market share, \ie the number of agents that \gaedit{choose them.}\gadelete{chose this principal.} Thus they aim to select the algorithm that maximizes their expected market share.

### 2021-01-19 journal paper/content/sec-theory.tex
more space saving edits

\begin{theorem}\label{thm:random-clean}
Fix a \HardMaxRandom response function $\respF$. Suppose algorithms \alg[1], \alg[2] are \bmonotone and $T$-oblivious, and \eqref{eq:random-assn} holds. If \alg[1] \emph{BIR-dominates} \alg[2] starting from step $n_0$, then each agent $t\geq \max(n_0,m_0)$ chooses principal $1$ with probability $\respF(1) = 1- \eps_0$ (which is the largest possible selection probability for this response function).
\end{theorem}

@@

\begin{corollary}\label{cor:random}
Fix a \HardMaxRandom response function $\respF$. Consider the competition game in which all feasible MAB algorithms are $T$-oblivious, \bmonotone, and satisfy \eqref{eq:random-assn} for some fixed $m_0$. Suppose some feasible algorithm \alg  BIR-dominates all other feasible algorithms, starting from some local step $n_0$. Then, for any sufficiently large time horizon $T$, this game has a unique Nash equilibrium, in which both principals choose algorithm \alg.
\end{corollary}

>>>>

\begin{theorem}\label{thm:random-clean}
Fix a \HardMaxRandom response function $\respF$. Suppose algorithms \alg[1], \alg[2] are \bmonotone and $T$-oblivious, and \eqref{eq:random-assn} holds. If \alg[1] \emph{BIR-dominates} \alg[2] starting from step $n_0$, then each agent $t\geq \max(n_0,m_0)$ chooses principal $1$ with probability $\respF(1) = 1- \eps_0$ (\gadelete{which is }the largest possible selection probability for this response function).
\end{theorem}

@@

\begin{corollary}\label{cor:random}
Fix a \HardMaxRandom response function $\respF$. Consider the competition game \gaedit{where}\gadelete{in which} all feasible MAB algorithms are $T$-oblivious, \bmonotone, and satisfy \eqref{eq:random-assn} for some fixed $m_0$. Suppose some feasible algorithm \alg  BIR-dominates all other feasible algorithms, starting from some local step $n_0$. Then, for any sufficiently large time horizon $T$, this game has a unique Nash equilibrium\gadelete{, in which}\gaedit{ where} both principals choose algorithm \alg.
\end{corollary}
